Universal Properties in Generalized Multicategories

### 2020-02-07 universal-properties/upgm.tex
delete failed agda syntax attempt and add note about polynomials

>>>>

\section{Polynomial Multicategories}

$T$-multicategories for an arbitrary monad on a virtual equipment are
maybe too general. Things get a bit more concrete if we consider the
case where $T$ is a \emph{polynomial monad}, and we can get a toy
theory by considering polynomials in \emph{one} variable, i.e., spans.

In this case, we consider the double category of polynomials in some
rich category $E$, whose 2-cells are given by cartesian
morphisms. Then we can define a \emph{flavor} of multicategory to just
be some (horizontal) monad $T : I \pto I$ in that double category, and
can define a $T$-multicategory to be a monad in the slice over
$T$. This makes our monad $T$ much more concrete: the object $I$ is an
object of \emph{sorts}, each ``shape'' gives us a \emph{judgment} of
our multicategory, and the positions in the shape tell us what the
free variables are. The monad structure gives us identity judgments
and the different cuts available between judgments (i.e., all of
them).
